%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Olufadeke Oladeji, MSN, RN-BSN} \\ \vspace{1pt}
    Raleigh, NC  $|$
    \small 972-302-8939 $|$
    \href{mailto:fadetoky@yahoo.com}{\underline{fadetoky@yahoo.com}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Walden University}{Minneapolis, Minnesota}
      {Master of Science in Nursing; Psychiatric-Mental Health Nurse Practitioner}{}
    \resumeSubheading
      {University of Texas}{Arlington, TX}
      {Bachelor of Science in Nursing; Registered Nurse}{}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
      \resumeSubheading
      {Primary Care Manager (RN)}{December 2017 -- January 2023}
      {Department of Veteran Affairs}{Full-Time}
      \resumeItemListStart
        \resumeItem{Utilized nursing process and evidence-based practice to collaborate with Patients, Health Technicians, and Providers  to develop a patient-driven holistic care plan}
        \resumeItem{Acted as a team leader and player to achieve desirable veterans’ outcomes and ensure policies, nursing practice, and  standards of care are being practiced correctly}
        \resumeItem{Attended and participated in bi-weekly huddles with PACT Team to initiate and implement an interdisciplinary plan of care based on assessments}
        \resumeItem{Assist with women's health procedures such as Pap smears, Nexplanon removal/placement, and colonoscopies. As well as performed EKGs routinely and for emergency situations.}
        \resumeItem{Communicated with patients utilizing the VA Video Connect System, as well as triage schedule and walk-in patients as needed}
        \resumeItem{Monitored patients at high risk for hospitalization and keep the Primary Care Provider apprised of clinical issues that may require provider intervention}
        \resumeItem{Collaborated with other multidisciplinary teams- pharmacist, nutritionist, MH clinicians, social workers, community care personnel, etc.}
      \resumeItemListEnd
    \resumeSubheading
      {Behavioral Health Nurse (RN)}{April 2021 - September 2022}
      {Maria Parham Health - Duke Lifepoint}{Full-Time}
      \resumeItemListStart
        \resumeItem{Triaging involuntary and voluntary clients with mental health and physical conditions.}
        \resumeItem{Completing crisis assessments of clients’ mental health concerns}
        \resumeItem{Administering oral, inhalation, and inject-able medications to patients}
        \resumeItem{Answering and directing calls of patients with mental health concerns/crises appropriately}
      \resumeItemListEnd
    \resumeSubheading
      {Emergency Response Nurse (RN)}{December 2014 -- September 2017}
      {Department of Veteran Affairs}{Full-Time}
      \resumeItemListStart
        \resumeItem{Administer medications orally, Intravenously-iv push or bolus, Injections- Sub-q or intramuscular under physician’s direction.}
        \resumeItem{Operating equipment such as EKG, Bladder scanner, DinaMap, Cardiac Monitor, POC A1c, Bhcg, Troponin, Chem.7, and insertion of Foley catheter (indwelling). Set up for Pap smear, Rectal exam, and Cervical exam.}
        \resumeItem{Triaging patients and providing proper emergency severity index (ESI) for each patient using critical thinking skills based on patient acuity, and doing focused assessments.}
        \resumeItem{Caring for the Veterans diagnosed with PTSD, SI and HI, depression, and anxiety or panic attacks.}
        \resumeItem{Collaborating with other emergency medical team members to plan, manage, and assess patient treatment.}
        \resumeItem{Delegating to other healthcare workers such as nursing assistants, RNs, and health technicians.}
        \resumeItem{Developing skills required for competent performance in an emergent situation.}
        \resumeItem{Supervising and guiding other staff members as an ED charge nurse.}
        \resumeItem{Managing admissions and discharges in the Emergency Department.}
      \resumeItemListEnd
      \resumeSubheading
      {Mental Health Rehabilitation Technician}{October 2008 -- December 2014}
      {Department of Veteran Affairs}{West Haven, CT}
      \resumeItemListStart
        \resumeItem{Performed a wide range of administrative support and patient care duties supported by the Ambulatory Care Product Line.}
        \resumeItem{Scheduling patients for appointments, sending out letters of notification to patients, ordering medical records, and checking in patients Answering telephone inquiries, resolving problems regarding scheduling, medications, provider contacts, etc.}
        \resumeItem{Performing vital sign readings including temperatures, blood pressure, pulse, finger pricks, height, and weight.}
        \resumeItem{Operating and monitoring commonly used electrocardiogram (EKG) equipment and accessories and performing other related duties as needed.}
        \resumeItem{Observed, monitored, and documented patients' status in CPRS, completed patient security checks, respond to crisis situations, and provide patient care treatments including restraint application as directed on a restricted unit.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd



%-----------PROGRAMMING SKILLS-----------
\section{Licensure and Certifications}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \textbf{Registered Nurse}{: North Carolina Board of Nursing}
    \newline\textbf{Basic Life Support}{: American Heart Association}
    }}
 \end{itemize}
%-------------------------------------------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \textbf{Telehealth, Video Care Connect System }
    $|$\textbf{ EKG, Triage, Bladder Scanner }
    $|$\textbf{ Oxygen Administration }
    $|$\textbf{ NG Tube Insertion }
    $|$\textbf{ Ventilator/Tracheotomy Care }
    $|$\textbf{ Discharge Instructions }
    $|$\textbf{ Colonoscopy }
    $|$ \textbf{ Pap Smear Setup }
    $|$ \textbf{ Phlebotomy }
    $|$ \textbf{ Nexplanon Removal/Placement }
    $|$ \textbf{ Medication Administration }
    $|$ \textbf{ Community Outpatient Referrals/Consults }
    $|$ \textbf{ Cardiac Monitoring }
    $|$ \textbf{ Catheter Insertion/Removal }
     $|$ \textbf{ Doximity }
     $|$ \textbf{ Doxy.me }
     $|$ \textbf{ UpToDate }
     $|$ \textbf{ Computerized Patient Record System }
     }}
 \end{itemize}
\end{document}
